---
title: "Acoustic diversity indices as biodiversity indicators: a meta-analysis"
subtitle: "Supplementary material"
header-includes:
   - \usepackage{booktabs}
   - \usepackage{colortbl}
   - \usepackage{float}
   - \usepackage[labelfont=bf]{caption}
output:
        pdf_document:
            number_sections: false
            latex_engine: xelatex
            keep_tex: true
---
 
\renewcommand{\figurename}{Supplementary Figure}
\renewcommand{\tablename}{Supplementary Table}

A neat presentation of the supplementary material can be found in \url{https://irene-alcocer.github.io/Acoustic-Indices/}

```{r, include = FALSE}
    knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, echo = FALSE)
```

```{r, warning = FALSE, message = FALSE, results = "hide"}
    require(knitr)
    require(png)
    require(dplyr)
    require(stringr)
    require(metafor)
    require(compute.es)
    require(kableExtra)
    require(pander)
    require(ggplot2)
    require(RColorBrewer)
  
    source("src/acoustic_indices_functions.R")
```

\section{Data descriptions}

\begin{figure}
    \includegraphics{"rmd/Fig.S1.png"}
    \caption{
        Temporal evolution (2007 – 2019) of the validation data from the total of 142 articles. Articles which correlate the acoustic indices with real biological data are represented with an orange line and studies which do not correlate with a green line
    }
\end{figure}

```{r tidydata, include = FALSE}
    df_raw <- read.csv("data/Table.S1.csv")
    n_used <- "n_adjusted"
    # Use n_adjusted as sample size
    df_tidy <- tidy_data(df_raw, n_used)
    # Studies database
    studies <- read.csv("data/Table.S2.csv")
    df_tidy <- merge(df_tidy, studies, by.x = "id", by.y = "ID", all.x = TRUE)
    df_tidy <- df_tidy %>% 
               mutate(authors = paste(Authors, year)) %>%
               select(id, entry, authors, everything(), -Publ_year, -Title,
                      -doi, -Authors) 
```

\begin{table}[!ht]
    \caption{Dataset used in the study. Due to the size of this table it is only available at https://irene-alcocer.github.io/Acoustic-Indices/}
\end{table}

\begin{table}[!ht]
    \caption{Variable descriptions for Supplementary Table 2. Available at https://irene-alcocer.github.io/Acoustic-Indices/}
\end{table}

```{r samplesizes_tables_studies}
studies_n <- as.data.frame(table(df_tidy$id), stringsAsFactors = FALSE)
studies_n <- cbind(unique(df_tidy$authors), studies_n)
colnames(studies_n) <- c("Study", "ID", "Effect_sizes")
studies_n <- studies_n %>%
              select(ID, Study, Effect_sizes) %>%
              arrange(-Effect_sizes)

kbl(studies_n, booktabs = TRUE, 
    caption = "Number of effect sizes collected from each of the 34 studies included in the meta-analysis. ID corresponds to the study identification number in our dataset") %>%
    kable_styling(latex_options = c("striped", "HOLD_position"), 
                                    full_width = FALSE) 
```

```{r samplesizes_tables_moderators, include = TRUE}
# Table for moderator levels
mods <- c("index", "bio", "diversity_source", "environ")
sample_sizes <- do.call(rbind, lapply(mods, function(x) n_studies_entries(df_tidy, x)))
# Format output
sample_sizes <- cbind(row.names(sample_sizes), sample_sizes)
sample_sizes <- as.data.frame(sample_sizes)
names(sample_sizes) <- c("Moderator_levels", "Effect_sizes", "Studies")
sample_sizes$Moderator_levels <- str_replace(sample_sizes$Moderator_levels, "^([a-z])", toupper)
n_row <- nrow(sample_sizes)
sample_sizes$Moderator_levels[(n_row - 1):n_row] <- c("Aquatic", "Terrestrial")
names(sample_sizes) <- c("Moderator levels", "Effect sizes", "Studies")

kbl(sample_sizes, booktabs = TRUE, row.names = FALSE, 
    caption = "Number of effect sizes and studies per moderator levels.") %>%
    kable_styling(latex_options = c("striped", "HOLD_position"), 
                                    full_width = FALSE) %>%
    row_spec(0, font_size = 12, bold = TRUE) %>%
    pack_rows("Acoustic indices", 1, 11) %>%
    pack_rows("Biodiversity metrics", 12, 16) %>%
    pack_rows("Diversity source", 17, 18) %>%
    pack_rows("Environment", 19, 20)
```

\begin{figure}[H]
    \includegraphics{"rmd/mapa.png"}
    \caption{
        The geographic distribution of the study sites corresponding to the 35 studies used in the literature review. The colouring of countries exhibits a white to black gradient relative to an increase in the number of studies contributed by each country. The coloured dots discriminate between different groups of studied taxa.
    }
\end{figure}


\begin{figure}[H]
    \includegraphics{"rmd/heatmap.png"}
    \caption{
        Distribution of the 35 articles by biodiversity parameters, taxa and acoustic indices studied. The graph shows the number of articles for each biodiversity parameter and taxonomic group for each acoustic diversity index.
    }
\end{figure}


\begin{figure}[H]
    \includegraphics{"rmd/ps.index.png"}
    \caption{
        Pseudoreplication summary. The data is representing the total number of articles for each index. Color orange represents number of pseudo-replicated studies and green non pseudo-replicated studies. The article (Papin et al., 2019b) was withdrawal from the pseudoreplication analysis due to impossibility of obtain the pseudoreplication data causing some variation on the total number of each acoustic index.
    }
\end{figure}

\clearpage

\section{Overall Effect Size}

\subsection{Model output}
```{r meta_overall, echo = TRUE}
res_main <- rma.mv(z, var, random = ~1 | id/entry, data = df_tidy)
res_main
```

```{r meta_overall_r}
r_main <- sapply(c(r = res_main$b, CI.lb = res_main$ci.lb, CI.ub = res_main$ci.ub), z2r)
r_main_pander <- r_main
names(r_main_pander) <- c("Estimate", names(r_main)[2:3])
r_main_pander <- as.data.frame(cbind(names(r_main_pander), round(r_main_pander, 2)))
colnames(r_main_pander) <- c("Parameter", "Value")
kbl(r_main_pander, booktabs = TRUE, row.names = FALSE,
    caption = "
        Resulting estimates from intercept-only model converted to Pearson's correlation. 'Estimate' is the Pearson's r summary effect size. 'CI.lb' and 'CI.ub' are the confidence intervals lower and upper bounds, respectively.
    ") %>%
    kable_styling(latex_options = c("striped", "HOLD_position"),
                                    full_width = FALSE) 
```

\subsection{Heterogeneity}

```{r meta_hetero}
Is <- multilevel_I(res_main) * 100
Is_df <- data.frame(Is[1], Is[2])
names(Is_df) <- c("Within study", "Between study")
rownames(Is_df) <- c("% Unexplained variation")
total_I <- paste("Total heterogeneity: ", round(Is[1] + Is[2], 2), "%")
header <- c(3)
names(header) <- c(total_I)
kbl(Is_df, booktabs = TRUE, digits = 2, 
    caption = "
        Uncounted heterogeneity of the intercept-only model as measured by $I^2$ statistic. Within study heterogeneity (level 2) corresponds to the uncounted variation that is found on effect sizes within studies, and between study heterogeneity corresponds to the uncounted variation between studies (level 3).
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

```{r dmetar_I, fig.align = "center", fig.pos = "H", fig.cap = "Visual representation of how variance was distributed over the multilevel structure of the intercept-only model. Within study heterogeneity (level 2) corresponds to the unnacounted variation that is found on effect sizes within studies, and between study heterogeneity corresponds to the unnacounted variation between studies (level 3)."}
mlm.variance.distribution(res_main)
```

\clearpage

\section{Subgroup analysis}

\subsection{Model output}

```{r df_meta_indices, include = FALSE, results = "hide"}
df_indices <-  clear_moderators(df_tidy, "index")
```

```{r meta_indices, echo = TRUE}
res_indices <- rma.mv(z, var, random = ~ 1 | id/entry, mods = ~ index - 1, data = df_indices)
res_indices
```

```{r meta_indices_tbl}
df_pred_indices <- get_predictions(res_indices, intercept = FALSE)
df_pred_indices$coef <- str_remove(df_pred_indices$coef, "index")
names(df_pred_indices) <- c("Index", "Estimate", "SE", "CI.lb", "CI.ub")
kbl(df_pred_indices, booktabs = TRUE, 
    caption = "
        Resulting estimates from sub-group analysis. The 'Estimate' column is the Pearson correlation effect size; SE is the standard error and CI.lb and CI.up, the lower and upper bounds of the confidence intervals, respectively.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```


\section{Meta-regression}

\subsection{Model output}

```{r df_meta_regression, include = FALSE, results = "hide"}
mods <- c("index", "bio", "environ", "diversity_source")
df_full <- clear_moderators(df_tidy, mods)
```

```{r meta_regression, echo = TRUE}
res_full <- rma.mv(z, var, random = ~1 | id/entry, 
                   mods = ~ index + bio + environ + diversity_source, 
                   data = df_full)
 
res_full
```

\subsection{Collinearity}

```{r collinearity}
vif_meta <- as.data.frame(vif.rma(res_full))
vif_meta <- tibble::rownames_to_column(vif_meta, "Moderators")
colnames(vif_meta)[2] <- "VIF" 
kbl(vif_meta, booktabs = TRUE, 
    caption = "
        VIF values obtained for each moderator level.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

\subsection{Visualization of results}

```{r mod_level_estimates}
df_pred_tbl <- get_predictions(res_full, format_table = TRUE, clean_labels = TRUE)
kbl(df_pred_tbl, booktabs = TRUE, 
    caption = "
        Table used to plot Supplementary Figure 6. Each estimate corresponds to the additive effect when a moderator level is replaced in the intercept (e.g. ADI is the additive effect of ADI when ADI is put as intercept instead of ACI). The column 'Coefficients' lists the model intercept and the levels of each moderator. The column 'Estimate' is the estimated Pearson (r) correlation. 'SE' is the standard error of the estimate. 'CI' are the [lower] [upper] bounds of the confidence intervals.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

```{r mod_level_estimates_plt, fig.width = 10, fig.height = 8, fig.pos = "H", fig.cap = "Estimates (circles) and corresponding 95% confidence intervals (horizontal lines). Moderator are acoustic indices (Index), biodiversity metrics (Bio), environment (Environment) and acoustic source (Source). Each estimate corresponds to the additive effect when a moderator level is replaced in the intercept (e.g. ADI is the additive effect of ADI when ADI is put as intercept instead of ACI).Estimated effect sizes whose 95% confidence intervals do not overlap zero (black vertical line) indicate a positive correlation between acoustic indices and diversity if they are to the right of zero, or a negative correlation if they are to the left of zero."}
df_pred <- get_predictions(res_full)
colnames(df_pred) <- tolower(str_remove(colnames(df_pred), "\\s.*"))
df_pred$moderators <- df_pred_tbl$Moderators
df_pred$coef <- factor(df_pred_tbl$Coefficients, 
                       levels = rev(df_pred_tbl$Coefficients))

plt_colors <- c("#000000", brewer.pal(n = 4, name = "Dark2"))
ggplot(data = df_pred, aes(x = z2r(estimate), y = coef, color = moderators)) + 
    geom_point(size = 3) +
    geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height = 0, size = 1) +
    geom_vline(xintercept = 0, linetype = 1) + 
    scale_color_manual(values = plt_colors, name = "Moderators") + 
    theme_minimal() + 
    xlab("Effect size (r)") +
    theme(axis.text.x = element_text(size = 13, color = "black"),
          axis.text.y = element_text(size = 13, color = "black"),
          axis.line.x = element_line(color = "black"),
          axis.line.y = element_line(color = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_text(size = 14),
          panel.grid.major.y = element_blank(),
          legend.title = element_text(hjust = 0.5, size = 14),
          legend.text = element_text(size = 14)
    )
```

\subsection{Test of moderators}

```{r test_moderators}
imp_mods <- matrix(nrow = length(mods) + 1, ncol = 4, 
                   dimnames = list(NULL, c("Moderator", "Q", "df", "p")))
imp_mods <- as.data.frame(imp_mods)
# Add importance of all moderators
imp_mods[1, 2:ncol(imp_mods)] <- res_full[c("QM", "m", "QMp")]
imp_mods$Moderator[1] <- "All moderators"

for(i in 2:nrow(imp_mods)){
  wald_test <- anova(res_full, 
                     btt=grep(mods[i - 1], rownames(res_full$b)))[c("QM", "m","QMp")]
  imp_mods[i, 2:ncol(imp_mods)] <- wald_test
}
imp_mods$Moderator[2:nrow(imp_mods)] <- c("Acoustic indices", 
                                          "Biodiv. parameters", 
                                          "Environment", "Diversity source")
imp_mods <- mutate_if(imp_mods, is.numeric, round, 3)

kbl(imp_mods, booktabs = TRUE, 
    caption = "
        Wald-type tests for all moderators (first row), and for each moderator separately (remaining rows). 'Q' is the Wald statistic. 'df' are the degrees of freedom. 'p' is the probability that moderator estimates came from a chi-square distribution, where all estimates are equal to zero. So a p-value < 0.05 gives support against the null hypothesis that moderator levels estimates are equal to zero (i.e. they do not explain variation in effect sizes).
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

\subsection{Contrasts between moderator levels}

\textbf{Contrasts between H and other acoustic indices}
```{r compare_indices_H}
# Test differences between H and other indices
H_comp <- compare_moderators(df_full, res_full, "index", "H")
kbl(H_comp, digits = 3, booktabs = TRUE,
    caption = "
        Wald-type tests for the constrasts between acoustic index H with all other acoustic indices. The column 'Compared' expresses the comparison, in this cases it is the difference between the estimate H and the estimate of each of the other acoustic indices. The column 'Estimate' is the estimate obtained from the difference expressed in the previous column. 'SE' is the standard error of the difference, and CI.lb, CI.up the confidence interval lower and upper bound, respectively. 'QM' is the Wald statistic. 'p' is the probability that the difference between estimates is equal to zero. Thus, a p-value < 0.05 gives support against the null hypothesis of no difference between the estimate of the H index and the estimate of the other index.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

\textbf{Contrasts between NDSI and other acoustic indices}
```{r compare_indices_NDSI}
NDSI_comp <- compare_moderators(df_full, res_full, "index", "NDSI")
kbl(NDSI_comp, digits = 3, booktabs = TRUE,
    caption = "
        Wald-type tests for the constrasts between acoustic index NDSI with all other acoustic indices. The column 'Compared' expresses the comparison, in this cases it is the difference between the estimate NDSI and the estimate of each of the other acoustic indices. The column 'Estimate' is the estimate obtained from the difference expressed in the previous column. 'SE' is the standard error of the difference, and CI.lb, CI.up the confidence interval lower and upper bound, respectively. 'QM' is the Wald statistic. 'p' is the probability that the difference between estimates is equal to zero. Thus, a p-value < 0.05 gives support against the null hypothesis of no difference between the estimate of the NDSI index and the estimate of the other index.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

\textbf{Contrasts between sound abundance and other biodiversity parameters}
```{r compare_bio}
sound_abund_comp <- compare_moderators(df_full, res_full, "bio", "sound_abundance")
kbl(sound_abund_comp, digits = 3, booktabs = TRUE,
    caption = "
        Wald-type tests for the contrasts between the biodiversity metric sound abundance with all other biodiversity parameters. The column 'Compared' expresses the comparison, in this cases it is the difference between the estimate sound abundance and the estimate of each of the other biodiversity metrics. The column 'Estimate' is the estimate obtained from the difference expressed in the previous column. 'SE' is the standard error of the difference, and CI.lb, CI.up the confidence interval lower and upper bound, respectively. 'QM' is the Wald statistic. 'p' is the probability that the difference between estimates is equal to zero. Thus, a p-value < 0.05 gives support against the null hypothesis of no difference between the estimate of the sound abundance metric and the estimate of the other metric.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

\clearpage

\section{Sensibility analysis}

\subsection{Cook's distance}

```{r cooks_dist_study, fig.height = 6, fig.pos = "h", fig.cap = "Cook's distance values for each study (blue dots on the figure) and average Cook's distance over all studies indicated as a dashed vertical red line. The Cook's distance for a given study can be interpreted as the distance between the entire set of predicted values once with this study included and once with the this study excluded from the model fitting procedure. On the y-axis are the studies identified by first author and year. The x-axis corresponds to the Cook's distance values."}

### Cook's distances for each study!
cooks_dist <- cooks.distance(res_full, cluster=df_full$id)
df_full$id <- as.character(df_full$id)

df_cooks <- data.frame(id = names(cooks_dist), cooks_dist = cooks_dist)

df_cooks <- df_cooks %>% 
              left_join(df_full, by = "id") %>%
              select(id, authors, cooks_dist)
# Remove leading spaces
df_cooks$authors <- str_remove(df_cooks$authors, "^\\s")
df_cooks <- df_cooks %>%
              filter(!duplicated(authors)) %>%
              arrange(authors)

ggplot(data = df_cooks, aes(x = authors, y = cooks_dist, group = 1)) + 
  geom_point(color = "deepskyblue4") +
  geom_line(color = "deepskyblue4") + 
  geom_segment(aes(xend=authors), yend = 0, color = "darkgrey", linetype = 2) + 
  geom_hline(yintercept = mean(cooks_dist), color = "darkred", linetype = 2) + 
  xlab("Studies") + ylab("Cook's Distance") + 
  scale_x_discrete(limits = rev(df_cooks$authors)) + 
  theme_minimal() + 
  theme(
        axis.text = element_text(color = "black"),
        axis.line = element_line(color = "black"),
  ) + 
  coord_flip() 

```

\clearpage

\subsection{Inspection of outliers}

```{r check_outliers, fig.height = 3, fig.pos = "H", fig.cap = "Boxplot and distribution of of effect size values (dots) of the two studies identified as outliers. The y-axis identifies the study, and the x-axis corresponds to the Pearson r effect size. The green vertical dashed line is the summary effect obtained in the intercept-only model."}
outliers <- df_cooks[which(df_cooks$cooks_dist > mean(df_cooks$cooks_dist)), ]$id

df_outliers <- df_full[which(df_full$id %in% outliers), ]

ggplot(data = df_outliers, aes(x = z2r(z), y = id)) + 
  geom_boxplot(aes(color = id), fill = NA, width = 0.3) + 
  geom_jitter(height = 0.1, aes(color = id)) + 
  scale_color_brewer(palette = "Set2") + 
  scale_y_discrete(labels = rev(unique(df_outliers$authors))) + 
  xlab("Effect size (r)") +
  geom_vline(xintercept = z2r(res_main$b), color = "chartreuse4", linetype = 2) + 
  theme_minimal() + 
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_text(size = 11, color = "black"),
    axis.text.x = element_text(size = 11, color = "black"),
    axis.line.x = element_line(color = "black"),
    legend.position = "none"
  )

```

\clearpage

\subsection{Model output without outliers}

```{r df_no_outliers}
df_no_outliers <- df_full[-which(df_full$id %in% outliers), ]
```

```{r no_outliers, echo = TRUE}
res_no_outliers <- rma.mv(z, var, random = ~1 | id/entry, 
                   mods = ~ index + bio + environ + diversity_source, 
                   data = df_no_outliers)
res_no_outliers
```

\clearpage

\subsection{Effect size tendencies}

\textbf{Relationship between effect size and journal impact factor}

```{r effect_size_impact_factor, fig.pos = "H", fig.cap = "Relation between effect size mean values (circles) and journal impact factor. Circle size indicates the relative sample size of each effect size. The fitted line is a simple least squares regression with the corresponding 95% confidence interval region in grey. The dashed horizontal line represents an effect size of 0. Effect size mean values are positioned along the impact factor axis with minor random noise to reduce overlapping."}
plt_color <- "deeppink4"
ggplot(df_tidy, aes(x = impact_factor, y = z2r(z))) + 
  geom_jitter(aes(size = n), shape = 21, 
              fill = alpha(plt_color, 0.5), 
              color = plt_color,
              width = 0.2) + 
    geom_hline(yintercept=0, linetype = 2) +
    geom_smooth(method='lm', color = plt_color) +
    labs(y = "Effect size (r)", x = "Impact Factor") +  
    theme_minimal() +
    theme(
        axis.line.y = element_line(color = "black"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 14),
        legend.position = "none"
    )
```
