---
title: "Acoustic indices as proxies for biodiversity: a meta-analysis"
subtitle: "Supporting information"
header-includes:
   - \usepackage{booktabs}
   - \usepackage{colortbl}
   - \usepackage{float}
   - \usepackage{caption}
   - \DeclareCaptionLabelFormat{Sfignum}{#1~S#2} 
   - \captionsetup{labelfont=bf, labelformat=Sfignum, labelsep=period, singlelinecheck=false}
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
author: "Irene Alcocer, Herlander Lima, Larissa S. M. Sugai, Diego Llusia"
output:
        pdf_document:
            number_sections: false
            latex_engine: xelatex
            keep_tex: true
---
 
\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Table}

A neat presentation of the supplementary material can be found in the online supplementary material at \url{https://irene-alcocer.github.io/Acoustic-Indices/}

```{r, include = FALSE}
    knitr::opts_chunk$set(cache = FALSE, warning = FALSE, message = FALSE, echo = FALSE)
```

```{r, warning = FALSE, message = FALSE, results = "hide", cache = FALSE}
    require(knitr)
    require(png)
    require(tidyverse)
    require(dplyr)
    require(stringr)
    require(metafor)
    require(compute.es)
    require(kableExtra)
    require(pander)
    require(ggplot2)
    require(ggtext)
    require(RColorBrewer)
  
    source("src/acoustic_indices_functions.R")
```

```{r tidydata, include = FALSE}
    df_raw <- read.csv("data/Table.S1.csv")
    n_used <- "n_adjusted"
    # Use n_adjusted as sample size
    df_tidy <- tidy_data(df_raw, n_used)
    # Studies database
    studies <- read.csv("data/Table.S2.csv")
    df_tidy <- merge(df_tidy, studies, by.x = "id", by.y = "ID", all.x = TRUE)
    df_tidy <- df_tidy %>% 
               mutate(authors = paste(Authors, year)) %>%
               select(id, entry, authors, everything(), -Publ_year, -Title,
                      -doi, -Authors) 
```

\begin{table}[!ht]
    \caption{Data set used in the study. Due to the size of this table it is only available at \url{https://irene-alcocer.github.io/Acoustic-Indices/index.html\#Dataset} }
    \label{table:dataset}
\end{table}

\begin{table}[h]
    \caption{Variable descriptions for Table S\ref{table:dataset}. Available at
     \url{https://irene-alcocer.github.io/Acoustic-Indices/index.html\#Dataset} }
\end{table}

```{r data_features_table}
feature_rows <- c(5, 4, 4, 4, 6, 11)
categories <- c("Publication", "Biological data", "Acoustic data", "Recording",
                "Sampling design", "Statistics")
features <- c("Authors", "Title", "Journal", "Year of publication", "Peer reviewed",
              "Environment", "Taxonomic group", "Diversity metric", "Diversity source",
              "Acoustic index", "Frequency range", "FFT size", "Noise treatment",
              "Sampling rate", "Audio format", "Recording length", "Recording method",
              "Study sites", "Distance between sites", "Recorders per site", "Recording days",
                "Daily period", "Daily sample",
              "Statistical test", "Independence", "R${^2}$", "r", "b", "t-statistic",
                "Standard error", "Sample size", "Pseudoreplication", "Pseudoreplication type",
                "Adjusted sample size")
descript_publ <- c("", "", "", "", "Whether the study was subjected to peer review (Yes or No)")
descript_bio_data <- c("Ecosystem type where recordings were collected (aquatic or terrestrial)",
                       "Primary studied group (invertebrates, fish, anurans, mammals, birds, or several)",
                       "Species abundance, species richness, species diversity, abundance of sounds, or diversity of sounds",
                       "Method applied to obtain the diversity metric (acoustic or non-acoustic)")
descript_acous_data <- c("ACI, AEI, ADI, AR, BIO, H, H\\textsubscript{t}, H\\textsubscript{f}, M, NP, or NDSI. See Table 2 for definitions of acoustic indices",
                         "Range (in Hz) used for index calculation",
                         "Window size of the Fast Fourier Transformation (FFT)",
                         "Audio pre-processing related to noise (noise filtering, noise addition, or exclusion of noisy recordings)")
descript_rec <- c("Number of audio samples per second (in kHz) used for index calculation",
                  "Format of audio files (.wav, .mp3, etc.)",
                  "Length of each recording (in seconds) used for index calculation",
                  "Non-programmed (continuous), programmed (periodic) or manual (by an operator)")
descript_sampling <- c("Number of study sites (= spatial replicates)",
                       "Minimum distance between study sites (in meters)",
                       "Number of recording units per study site",
                       "Number of recording days per study site (= temporal replicates)",
                       "Period recorded within the day (dawn, morning, midday, evening, dusk, night, or all day)",
                       "Number of recordings collected within a day per study site")
descript_stats <- c("Statistical analysis used to test the relationship between acoustic indices and diversity metrics",
                    "Whether the statistical test was considered independent from other tests of the same study ",
                    "Coefficient of determination (for regression analysis)",
                    "Correlation coefficient (for Pearson or Spearman correlation)",
                    "Regression coefficient (for linear regression analysis)",
                    "Statistic value for Student’s \\textit{t}-test",
                    "Standard error of the test coefficient",
                    "Number of observations included in the statistical test",
                    "Inadequate specification of the number of true replicates in the statistical test (Yes or No)",
                    "Spatial, temporal, or spatial–temporal pseudoreplication",
                    "Suitable specification of the number of true replicates (for pseudoreplicated studies)")
descriptions <- c(descript_publ, descript_bio_data, descript_acous_data,
                  descript_rec, descript_sampling, descript_stats)
features_tbl <- data.frame(Category = rep(categories, feature_rows),
                           Features = features,
                           Description = descriptions)
kbl(features_tbl, booktabs = TRUE, escape = FALSE,
    caption = "List of the 34 features used to characterise studies that tested the relationship between acoustic indices and diversity metrics.") %>%
   kable_styling(latex_options = c("scale_down", "HOLD_position")) %>%
   row_spec(0, font_size = 12, bold = TRUE) %>%
   column_spec(1, bold = TRUE) %>%
   row_spec(c(1:5, 10:13, 18:23) - 1, extra_latex_after = "\\rowcolor{gray!6}") %>%
   collapse_rows(columns = 1, latex_hline = "major", 
                 valign = "top")

```

```{r samplesizes_tables_studies}
studies_n <- as.data.frame(table(df_tidy$id), stringsAsFactors = FALSE)
studies_n <- cbind(unique(df_tidy$authors), studies_n)
colnames(studies_n) <- c("Study", "ID", "Effect_sizes")
studies_n <- studies_n %>%
              select(ID, Study, Effect_sizes) %>%
              arrange(-Effect_sizes)
colnames(studies_n) <- c("ID", "Study", "Number of effect sizes")
studies_n$Study <- author_format(studies_n$Study, markup = "latex")

kbl(studies_n, booktabs = TRUE, escape = FALSE,
    caption = "Number of effect sizes collected from each of the 34 studies included in the meta-analysis. ID corresponds to the study identification number in our data set.")  %>%
    kable_styling(latex_options = c("striped", "HOLD_position"), 
                                    full_width = FALSE) 
```

```{r samplesizes_tables_moderators, include = TRUE}
# Table for moderator levels
mods <- c("index", "bio", "diversity_source", "environ")
sample_sizes <- do.call(rbind, lapply(mods, function(x) n_studies_entries(df_tidy, x)))
# Format output
sample_sizes <- cbind(row.names(sample_sizes), sample_sizes)
sample_sizes <- as.data.frame(sample_sizes)
names(sample_sizes) <- c("Moderator_levels", "Effect_sizes", "Studies")
sample_sizes$Moderator_levels <- str_replace(sample_sizes$Moderator_levels,
                                             "^([a-z])", toupper)
sample_sizes$Moderator_levels[12:16] <- c("Species abundance", "Species diversity",
                                          "Species richness", "Abundance of sounds",
                                          "Diversity of sounds")
sample_sizes$Moderator_levels[18] <- "Non-acoustic"
n_row <- nrow(sample_sizes)
sample_sizes$Moderator_levels[(n_row - 1):n_row] <- c("Aquatic", "Terrestrial")
sample_sizes$Moderator_levels <- str_replace(sample_sizes$Moderator_levels,
                                             "Hf", "H\\\\textsubscript{f}")
sample_sizes$Moderator_levels <- str_replace(sample_sizes$Moderator_levels,
                                             "Ht", "H\\\\textsubscript{t}")
names(sample_sizes) <- c("Moderator levels", "Effect sizes", "Studies")

kbl(sample_sizes, booktabs = TRUE, row.names = FALSE, escape = FALSE,
    caption = "Number of effect sizes and studies per moderator levels. See Table 2 for definitions of acoustic indices.") %>%
    kable_styling(latex_options = c("striped", "HOLD_position"), 
                                    full_width = FALSE) %>%
    row_spec(0, font_size = 12, bold = TRUE) %>%
    pack_rows("Acoustic indices", 1, 11) %>%
    pack_rows("Diversity metrics", 12, 16) %>%
    pack_rows("Diversity source", 17, 18) %>%
    pack_rows("Environment", 19, 20)
```

\begin{figure}[H]
    \includegraphics{"rmd/ps.index.png"}
    \caption{
        Pseudoreplication summary. The data represent the total number of articles for each index. Orange dots represent the number of  studies with pseudoreplication and green are without pseudoreplication. One article (Papin et al., 2019) was withdrawn from the pseudoreplication analysis as it was impossible to obtain data on pseudoreplication, thus leading to some variation in the total for each acoustic index. See Table 2 for definitions of acoustic indices.}
\end{figure}

```{r df_meta_regression, include = FALSE, results = "hide"}
mods <- c("index", "bio", "environ", "diversity_source")
df_full <- clear_moderators(df_tidy, mods)
```

```{r meta_regression, echo = FALSE}
res_full <- rma.mv(z, var, random = ~1 | id/entry, 
                   mods = ~ index + bio + environ + diversity_source, 
                   data = df_full)
#res_full
#
# Table is Table 4
#res_full_tbl <- model_res_table(res_full)
#kable(res_full_tbl, digits = 3, align = "lrrc", booktabs = TRUE,
#      caption = "Model estimates for the meta-regression over the data set without outliers. All values are Pearson correlation \\textit{r}. Full model output can be found in the online supplementary material.") %>%
#  kable_styling(latex_options = c("striped", "HOLD_position"),
#                full_width = FALSE) %>%
#   row_spec(0, bold = TRUE) 
```

```{r collinearity}
vif_meta <- vif.rma(res_full, table = TRUE)$vif["vif"][-1, , drop = FALSE]
vif_meta <- tibble::rownames_to_column(vif_meta, "Moderators")
colnames(vif_meta)[2] <- "VIF" 
vif_meta$VIF <- round(vif_meta$VIF, 3)
vif_meta$Moderators <- str_remove(vif_meta$Moderators, "index|bio|environ|diversity_source")
vif_meta$Moderators <- final_mod_names(vif_meta$Moderators)
kbl(vif_meta, booktabs = TRUE, 
    caption = "
        VIF (Variance Inflation Factor) values obtained for each moderator level. See Table 2 for definitions of acoustic indices.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"),
                full_width = FALSE) %>%
   row_spec(0, bold = TRUE) 
```

\clearpage

```{r meta_overall, echo = FALSE}
res_main <- rma.mv(z, var, random = ~1 | id/entry, data = df_tidy)
#res_main

res_main_tbl <- model_res_table(res_main, y_labels = "Overall effect")
colnames(res_main_tbl)[1] <- ""
kable(res_main_tbl, digits = 3, align = "lrrc", booktabs = TRUE,
      caption = "Model estimates for the intercept-only model. All values are Pearson correlation \\textit{r}. SE is the standard error and CI the confidence interval. Full model output can be found in the online supplementary material.") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"),
                full_width = FALSE) %>%
   row_spec(0, bold = TRUE) 

```

```{r dmetar_I, fig.align = "center", fig.pos = "H", fig.cap = "Visual representation of the distribution of variance over the multilevel structure of the intercept-only model. Within-study heterogeneity (level 2) corresponds to the unaccounted for variation that is found on effect sizes within studies, and between-study heterogeneity corresponds to the unaccounted for variation between studies (level 3)."}
mlm.variance.distribution(res_main)
```

```{r df_meta_indices, include = FALSE, results = "hide"}
df_indices <-  clear_moderators(df_tidy, "index")
```

```{r meta_indices, echo = FALSE}
res_indices <- rma.mv(z, var, random = ~ 1 | id/entry, mods = ~ index - 1, data = df_indices)
#res_indices

res_indices_tbl <- model_res_table(res_indices,
                                   y_labels = c(
                                     "ACI", "Index ADI", "Index AEI",
                                     "Index AR", "Index BIO", "Index H",
                                     "Index NDSI")
                                   )
colnames(res_indices_tbl)[1] <- "Index"
kable(res_indices_tbl, digits = 3, align = "lrrc", booktabs = TRUE,
      caption = "Model estimates for the sub-group analysis. All values are Pearson correlation \\textit{r}. SE is the standard error and CI the confidence interval. See Table 2 for definitions of acoustic indices. Full model output can be found in the online supplementary material.") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"),
                full_width = FALSE) %>%
   row_spec(0, bold = TRUE) 
```

\clearpage

```{r subgroup_plt, fig.pos = "H", fig.cap = "Effect size mean estimates (circles) and corresponding 95% confidence intervals (horizontal lines) obtained from the sub-group meta-analysis with acoustic indices as the moderating factor. Estimated effect sizes whose 95% confidence intervals do not overlap zero (black vertical line) indicate a positive correlation between acoustic indices and diversity if they are to the right of zero, or a negative correlation if they are to the left of zero. The dashed green vertical line represents the summary effect size obtained from the intercept only meta-analysis."}
nentries_index <- rowSums(table(df_indices$index, df_indices$id))
nstudies_index <- rowSums(ifelse(table(df_indices$index, df_indices$id) > 0, 1, 0))
n_index <- paste0(nentries_index, " (", nstudies_index, ")")

df_indices_plt <- data.frame("index" = names(nstudies_index),
                             "es" = z2r(res_indices$beta), 
                             "se" = z2r(res_indices$se), 
                             "ci.lb" = z2r(res_indices$ci.lb),
                             "ci.ub" = z2r(res_indices$ci.ub),
                             "n" = nstudies_index)

ggplot(data = df_indices_plt, aes(x = es, y = index)) + 
    geom_point(aes(color = index), size = 4) +
    geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub, color= index),
                   height = 0) + 
    geom_vline(xintercept = 0, linetype = 1) +
    geom_vline(xintercept = z2r(res_main$b), color = "forestgreen", 
               linetype = 2) + 
    scale_y_discrete(limits = rev(df_indices_plt$index)) +
    scale_color_brewer(palette="Dark2") +
    xlab(expression(paste("Effect size (", italic("r"), ")"))) +
    theme_minimal() + 
    theme(axis.text.x = element_text(size = 12, color = "black"),
          axis.text.y = element_text(size = 13, color = "black"),
          axis.line.x = element_line(color = "black"),
          axis.line.y = element_line(color = "black"),
          axis.title.x = element_text(size = 14),
          axis.title.y = element_blank(),
          legend.position = "none"
    )
```


```{r test_moderators}
imp_mods <- matrix(nrow = length(mods) + 1, ncol = 4, 
                   dimnames = list(NULL, c("Moderator", "\\textit{Q}",
                                           "df", "\\textit{p}")))
imp_mods <- as.data.frame(imp_mods)
# Add importance of all moderators
imp_mods[1, 2:ncol(imp_mods)] <- res_full[c("QM", "m", "QMp")]
imp_mods$Moderator[1] <- "All moderators"

for(i in 2:nrow(imp_mods)){
  wald_test <- anova(res_full, 
                     btt=grep(mods[i - 1], rownames(res_full$b)))[c("QM", "m","QMp")]
  imp_mods[i, 2:ncol(imp_mods)] <- wald_test
}
imp_mods$Moderator[2:nrow(imp_mods)] <- c("Acoustic indices", 
                                          "Diversity metrics", 
                                          "Environment", "Diversity source")
kbl(imp_mods, digits = 3, booktabs = TRUE, escape = FALSE,
    caption = "
       Results of Wald-type tests for all moderators (first row), and for each moderator separately (remaining rows). ``Q\" is the Wald statistic; ``df\" are the degrees of freedom; and ``p\" is the probability that moderator estimates came from a chi-square distribution, where all estimates are equal to zero. Thus p < 0.05 provides support against the null hypothesis that moderator levels estimates are equal to zero (i.e. they do not explain variation in effect sizes).
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) %>%
   row_spec(0, bold = TRUE) 
```


```{r compare_indices_H}
# Test differences between H and other indices
H_comp <- compare_moderators(df_full, res_full, "index", "H")
kbl_align <- ifelse(unlist(lapply(H_comp, is.numeric)), "r", "l")
H_comp <- mutate_if(H_comp, is.numeric, place_minus)

kbl(H_comp, digits = 3, booktabs = TRUE, escape = FALSE,
    align = kbl_align,
    caption = "
        Results of Wald-type tests for the contrasts between acoustic index H and all other acoustic indices. The column ``Compared\" expresses the difference between the estimate for H and the estimate of each of the other acoustic indices. The column ``Estimate\" is the estimate obtained from the difference shown in the previous column. ``SE\" is the standard error of the difference, and CI.lb, CI.ub the confidence interval lower and upper bound, respectively. ``Q\\textsubscript{m}\" is the Wald statistic; ``p\" is the probability that the difference between estimates is equal to zero. Thus, p < 0.05 gives support against the null hypothesis of no difference between the estimate of the H index and the estimate of the other index.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) %>%
   row_spec(0, bold = TRUE) 
```

```{r compare_indices_NDSI}
NDSI_comp <- compare_moderators(df_full, res_full, "index", "NDSI")
kbl_align <- ifelse(unlist(lapply(NDSI_comp, is.numeric)), "r", "l")
NDSI_comp <- mutate_if(NDSI_comp, is.numeric, place_minus)
kbl(NDSI_comp, digits = 3, booktabs = TRUE, escape = FALSE,
    align = kbl_align,
    caption = "
         Results of Wald-type tests for the contrasts between acoustic index NDSI and all other acoustic indices. The column ``Compared\" expresses the difference between the estimate NDSI and the estimate of each of the other acoustic indices. The column ``Estimate\" is the estimate obtained from the difference expressed in the previous column; ``SE\" is the standard error of the difference, and CI.lb, CI.ub the confidence interval lower and upper bound, respectively; ``Q\\textsubscript{m}\" is the Wald statistic; ``p\" is the probability that the difference between estimates is equal to zero. Thus, a p < 0.05 gives support against the null hypothesis of no difference between the estimate of the NDSI index and the estimate of the other index.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) %>%
   row_spec(0, bold = TRUE) 
```

```{r compare_bio}
sound_abund_comp <- compare_moderators(df_full, res_full, "bio", "sound_abundance")
sound_abund_comp$Compared <- c("Abundance of sounds - Species abundance",
                               "Abundance of sounds - Species diversity",
                               "Abundance of sounds - Species richness")
kbl_align <- ifelse(unlist(lapply(sound_abund_comp, is.numeric)), "r", "l")
sound_abund_comp <- mutate_if(sound_abund_comp, is.numeric, place_minus)
kbl(sound_abund_comp, digits = 3, booktabs = TRUE, escape = FALSE,
    align = kbl_align,
    caption = "
         Results of Wald-type tests for the contrasts between the diversity metric ``abundance of sounds\" and all other diversity metrics. The column ``Compared\" expresses the difference between the estimate ``abundance of sounds\" and the estimate of each of the other diversity metrics. The column ``Estimate\" is the estimate obtained from the difference shown in the previous column; ``SE\" is the standard error of the difference, and CI.lb, CI.ub the confidence interval lower and upper bound, respectively; ``Q\\textsubscript{m}\" is the Wald statistic; ``p\" is the probability that the difference between estimates is equal to zero. Thus, a p < 0.05 gives support against the null hypothesis of no difference between the estimate of the abundance of sounds metric and the estimate of the other metric.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) %>%
   row_spec(0, bold = TRUE) 
  
```

\clearpage

```{r pseudoreplication_moderator, echo = FALSE}
df_pseudorep <-  clear_moderators(df_tidy, "pseudoreplication", verbose = FALSE)  
  
res_pseudorep <- rma.mv(z, var, random = ~1 | id/entry, mods = ~ pseudoreplication, 
                        data = df_pseudorep)
#res_pseudorep
res_pseudorep_tbl <- model_res_table(res_pseudorep,
                                     y_labels = c("Intercept",
                                                  "Mod Pseudoreplicated"))
kable(res_pseudorep_tbl, digits = 3, align = "lrrc", booktabs = TRUE,
      caption = "Model estimates for the meta-analysis inspecting differences between pseudoreplicated and non-pseudoreplicated studies. The intercept correspond to the non-pseudoreplicated effect sizes. All values are Pearson correlation \\textit{r}. SE is the standard error, CI the confidence interval. Full model output can be found in the online supplementary material") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"),
                full_width = FALSE) %>%
   row_spec(0, bold = TRUE) 
```

```{r effect_size_impact_factor, fig.pos = "H", fig.cap = "Relationship between reported mean effect sizes and journal impact factor. Circle size indicates the relative sample size for each effect size. The fitted line is a meta-regression over the journal impact factor with the corresponding 95% confidence interval region shaded grey. The dashed horizontal line represents an effect size of 0. Effect size mean values are positioned along the impact factor axis with minor random noise to reduce overlapping. Model statistics in Pearson correlation \\textit{r} estimate [CI], intercept 0.40 [0.10, 0.63], slope --0.01 [--0.10, 0.08]. Full model output can be found in the online supplementary material"}
df_tidy_if <- filter(df_tidy, !is.na(impact_factor))
lin <- rma.mv(z, var, random = ~ 1 | id/entry, mods = ~ impact_factor, data = df_tidy_if)
preds <- predict(lin, interval = "confidence")
df_tidy_if$y <- z2r(preds$pred)
df_tidy_if$ymin <- z2r(preds$ci.lb)
df_tidy_if$ymax<- z2r(preds$ci.ub)

plt_color <- "deeppink4"
ggplot(df_tidy_if, aes(x = impact_factor, y = z2r(z))) + 
  geom_jitter(aes(size = n), shape = 21, 
              fill = alpha(plt_color, 0.5), 
              color = plt_color,
              width = 0.2) + 
    geom_hline(yintercept=0, linetype = 2) +
    geom_line(aes(y = y, x = impact_factor), color = plt_color) + 
    geom_ribbon(aes(ymin = ymin, ymax = ymax), alpha = 0.3) +
    labs(y = expression(paste("Effect size (", italic("r"), ")")), x = "Impact Factor") +  
    theme_minimal() +
    theme(
        axis.line.y = element_line(color = "black"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 14),
        legend.position = "none"
    )

#print(summary(lin))
#print(z2r(coefficients(lin)))
#print(z2r(lin$ci.lb))
#print(z2r(lin$ci.ub))
```

\clearpage

```{r cooks_dist_study, dev ="cairo_pdf", fig.height = 6, fig.pos = "h", fig.cap = "Cook's distance values for each study (blue dots) and average Cook's distance over all studies (dashed vertical red line). The Cook's distance for a given study can be interpreted as the distance between the entire set of predicted values with this study included and when this study is excluded from the model fitting procedure."}

### Cook's distances for each study!
cooks_dist <- cooks.distance(res_full, cluster=df_full$id)
df_full$id <- as.character(df_full$id)

df_cooks <- data.frame(id = names(cooks_dist), cooks_dist = cooks_dist)

df_cooks <- df_cooks %>% 
              left_join(df_full, by = "id") %>%
              select(id, authors, cooks_dist)
# Remove leading spaces
df_cooks$authors <- str_remove(df_cooks$authors, "^\\s")
df_cooks <- df_cooks %>%
              filter(!duplicated(authors)) %>%
              arrange(authors)
df_cooks$authors <- author_format(df_cooks$authors)
ggplot(data = df_cooks, aes(x = authors, y = cooks_dist, group = 1)) + 
  geom_point(color = "deepskyblue4") +
  geom_line(color = "deepskyblue4") + 
  geom_segment(aes(xend=authors), yend = 0, color = "darkgrey", linetype = 2) + 
  geom_hline(yintercept = mean(cooks_dist), color = "darkred", linetype = 2) + 
  xlab("Studies") + ylab("Cook\u2019s distance") + 
  scale_x_discrete(limits = rev(df_cooks$authors)) + 
  theme_minimal() + 
  theme(
        axis.line = element_line(color = "black"),
        axis.text.y = element_markdown(color = "black"),
        axis.text.x = element_text(color = "black", size = 8),
  ) + 
  coord_flip() 
```

\clearpage


```{r check_outliers, dev = "pdf", fig.pos = "H", fig.cap = "Boxplot and distribution of effect size values (dots) of the two studies identified as outliers. The x-axis shown is the Pearson \\textit{r} effect size. The green vertical dashed line is the summary effect obtained in the intercept-only model."}
outliers <- df_cooks[which(df_cooks$cooks_dist > mean(df_cooks$cooks_dist)), ]$id

df_outliers <- df_full[which(df_full$id %in% outliers), ]

df_outliers$authors <- author_format(df_outliers$authors)
ggplot(data = df_outliers, aes(x = z2r(z), y = id)) + 
  geom_boxplot(aes(color = id), fill = NA, width = 0.3) + 
  geom_jitter(height = 0.1, aes(color = id)) + 
  scale_color_brewer(palette = "Set2") + 
  scale_y_discrete(labels = rev(unique(df_outliers$authors))) + 
  xlab(expression(paste("Effect size (", italic("r"), ")"))) +
  geom_vline(xintercept = z2r(res_main$b), color = "chartreuse4", linetype = 2) + 
  theme_minimal() + 
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(size = 11, color = "black"),
    axis.text.x = element_text(size = 11, color = "black"),
    axis.line.x = element_line(color = "black"),
    legend.position = "none"
  )

```

```{r df_no_outliers}
df_no_outliers <- df_full[-which(df_full$id %in% outliers), ]
```

```{r no_outliers, echo = FALSE}
res_no_outliers <- rma.mv(z, var, random = ~1 | id/entry, 
                   mods = ~ index + bio + environ + diversity_source, 
                   data = df_no_outliers)
#res_no_outliers
res_no_outliers_tbl <- model_res_table(res_no_outliers)
res_no_outliers_tbl$Coefficients <- final_mod_names(res_no_outliers_tbl$Coefficients)
kable(res_no_outliers_tbl, digits = 3, align = "lrrc", booktabs = TRUE,
      caption = "Model estimates for the meta-regression over the data set without outliers. All values are Pearson correlation \\textit{r}. SE is the standard error, CI the confidence interval. Full model output can be found in the online supplementary material.") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"),
                full_width = FALSE) %>%
   row_spec(0, bold = TRUE) 
```

\clearpage

```{r outliers_model_plt, fig.pos = "ht", fig.cap = "Contrast of model estimates obtained with meta-regression analysis using the full data set (yellow) and over the data set with outliers removed (blue). Estimates are represented by circles and corresponding 95% confidence intervals by horizontal lines. Each estimate (except the intercept) corresponds to the additive effect of each coefficient as obtained with the \\textit{predict\\_rma} function from \\textit{metafor} R package. Estimated effect sizes whose 95% confidence intervals do not overlap zero (black vertical line) indicate a positive correlation between acoustic indices and diversity if they are to the right of zero, or a negative correlation if they are to the left of zero. We considered as outliers every study that had a Cook’s distance value higher than the mean of all Cook distances (see Fig.S5). Model moderators were acoustic indices (ADI, AEI, AR, BIO, H, NDSI, with ACI as intercept), diversity metric (Species abundance, Species diversity, Abundance of sounds, with Species richness as intercept), environment (Aquatic, with Terrestrial as intercept), diversity source (Acoustic, with Non-Acoustic as intercept). The solid vertical black line represents a null effect size. See Table 2 for definitions of acoustic indices."}

df_pred_tbl <- get_predictions(res_full, format_table = TRUE, clean_labels = TRUE)
df_pred_tbl$Coefficients <- final_mod_names(df_pred_tbl$Coefficients)
df_pred <- get_predictions(res_full)
colnames(df_pred) <- tolower(str_remove(colnames(df_pred), "\\s.*"))
df_pred$moderators <- df_pred_tbl$Moderators
df_pred$coef <- factor(df_pred_tbl$Coefficients, 
                       levels = rev(df_pred_tbl$Coefficients))

# With outliers results from full model results 
df_pred$df <- "with_outliers"
# No outliers resuls in dataframe
df_no_outliers_plt <- get_predictions(res_no_outliers)
df_no_outliers_plt$moderators <- df_pred$moderators
df_no_outliers_plt$coef <- factor(df_pred$coef, 
                                  levels = rev(df_pred$coef))
df_no_outliers_plt$df <- "no_outliers"

df_examine_outliers <- rbind(df_pred, df_no_outliers_plt)

plt_colors <- c("skyblue4", "goldenrod3")#"seagreen")
pd <- position_dodge(0.6)
n_rows <- nrow(res_full$b)

ggplot(data = df_examine_outliers, aes(x = estimate, y = coef, color = df, position = df)) + 
    geom_point(position = pd, size = 2.3) +
    geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height = 0, position = pd, size = 0.8) + 
    geom_vline(xintercept = 0, linetype = 1, color = "black") + 
    #scale_y_discrete(labels =  rev(y_labels)) +
    scale_color_manual(values = plt_colors, name = "Dataset", 
                       labels = c("No outliers", "Full data set")) + 
    geom_hline(yintercept= seq(1, n_rows - 1) + 0.5, linetype = 3, color = "black") + 
    theme_minimal() + 
    xlab(expression(paste("Effect size (", italic("r"), ")"))) +
    theme(axis.text.x = element_text(size = 12, color = "black"),
          axis.text.y = element_text(size = 12, color = "black"),
          axis.line.x = element_line(color = "black"),
          axis.line.y = element_line(color = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_text(size = 14),
          panel.grid.major.y = element_blank(),
          legend.title = element_blank(),
          legend.text = element_text(size = 11),
          legend.position = "top"
    )
```
