---
title: "Acoustic indices as proxies for biodiversity: a meta-analysis"
subtitle: "Supplementary material"
header-includes:
   - \usepackage{booktabs}
   - \usepackage{colortbl}
   - \usepackage{float}
   - \usepackage[labelfont=bf]{caption}
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
output:
        pdf_document:
            number_sections: false
            latex_engine: xelatex
            keep_tex: true
---
 
\renewcommand{\figurename}{Supplementary Figure}
\renewcommand{\tablename}{Supplementary Table}

A neat presentation of the supplementary material can be found in \url{https://irene-alcocer.github.io/Acoustic-Indices/}

```{r, include = FALSE}
    knitr::opts_chunk$set(cache = FALSE, warning = FALSE, message = FALSE, echo = FALSE)
```

```{r, warning = FALSE, message = FALSE, results = "hide", cache = FALSE}
    require(knitr)
    require(png)
    require(dplyr)
    require(stringr)
    require(metafor)
    require(compute.es)
    require(kableExtra)
    require(pander)
    require(ggplot2)
    require(RColorBrewer)
  
    source("src/acoustic_indices_functions.R")
```

\section{Data descriptions}

```{r tidydata, include = FALSE}
    df_raw <- read.csv("data/Table.S1.csv")
    n_used <- "n_adjusted"
    # Use n_adjusted as sample size
    df_tidy <- tidy_data(df_raw, n_used)
    # Studies database
    studies <- read.csv("data/Table.S2.csv")
    df_tidy <- merge(df_tidy, studies, by.x = "id", by.y = "ID", all.x = TRUE)
    df_tidy <- df_tidy %>% 
               mutate(authors = paste(Authors, year)) %>%
               select(id, entry, authors, everything(), -Publ_year, -Title,
                      -doi, -Authors) 
```

\begin{table}[!ht]
    \caption{Dataset used in the study. Due to the size of this table it is only available at https://irene-alcocer.github.io/Acoustic-Indices/}
\end{table}

\begin{table}[!ht]
    \caption{Variable descriptions for Supplementary Table 1. Available at https://irene-alcocer.github.io/Acoustic-Indices/}
\end{table}

```{r data_features_table}
feature_rows <- c(5, 4, 4, 4, 6, 11)
categories <- c("Publication", "Biological data", "Acoustic data", "Recording",
                "Sampling design", "Statistics")
features <- c("Authors", "Title", "Journal", "Year of publication", "Peer reviewed",
              "Environment", "Taxonomic group", "Diversity metric", "Diversity source",
              "Acoustic index", "Frequency range", "FFT size", "Noise treatment",
              "Sampling rate", "Audio format", "Recording length", "Recording method",
              "Study sites", "Distance between sites", "Recorders per site", "Recording days",
                "Daily period", "Daily sample",
              "Statistical test", "Independence", "R${^2}$", "r", "b", "t-statistic",
                "Standard error", "Sample size", "Pseudoreplication", "Pseudoreplication type",
                "Adjusted sample size")
descript_publ <- c("", "", "", "", "Whether the study was subjected to peer review (Yes or No)")
descript_bio_data <- c("Ecosystem type where recordings were collected (aquatic or terrestrial)",
                       "Primary studied group (invertebrates, fish, anurans, mammals, birds, or several)",
                       "Species abundance, species richness, species diversity, abundance of sounds, or diversity of sounds",
                       "Method applied to obtain the diversity metric (acoustic or non-acoustic)")
descript_acous_data <- c("ACI, AEI, ADI, AR, BIO, H, Ht, Hf, M, NP, or NSDI",
                         "Range (in Hz) used for index calculation",
                         "Window size of the Fast Fourier Transformation (FFT)",
                         "Audio pre-processing related to noise (noise filtering, noise addition, or exclusion of noisy recordings)")
descript_rec <- c("Number of audio samples per second (in kHz) used for index calculation",
                  "Format of audio files (.wav, .mp3, etc.)",
                  "Length of each recording (in seconds) used for index calculation",
                  "Non-programmed (continuous), programmed (periodic) or manual (by an operator)")
descript_sampling <- c("Number of study sites (= spatial replicates)",
                       "Minimum distance between study sites (in meters)",
                       "Number of recording units per study site",
                       "Number of recording days per study site (= temporal replicates)",
                       "Period recorded within the day (dawn, morning, midday, evening, dusk, night, or all day)",
                       "Number of recordings collected within a day per study site")
descript_stats <- c("Statistical analysis used to test the relationship between acoustic indices and diversity metrics",
                    "Whether the statistical test was considered independent from other tests of the same study ",
                    "Coefficient of determination (for regression analysis)",
                    "Correlation coefficient (for Pearson or Spearman correlation)",
                    "Regression coefficient (for linear regression analysis)",
                    "Statistic value for Student’s t-test",
                    "Standard error of the test coefficient",
                    "Number of observations included in the statistical test",
                    "Inadequate specification of the number of true replicates in the statistical test (Yes or No)",
                    "Spatial, temporal, or spatial-temporal pseudoreplication",
                    "Suitable specification of the number of true replicates (for pseudoreplicated studies)")
descriptions <- c(descript_publ, descript_bio_data, descript_acous_data,
                  descript_rec, descript_sampling, descript_stats)
features_tbl <- data.frame(Category = rep(categories, feature_rows),
                           Features = features,
                           Description = descriptions)
kbl(features_tbl, booktabs = TRUE, escape = FALSE,
    caption = "List of the 35 features used to characterize studies that tested the relationship between acoustic indices and diversity metrics.") %>%
   kable_styling(latex_options = c("scale_down", "HOLD_position")) %>%
   row_spec(0, font_size = 12, bold = TRUE) %>%
   column_spec(1, bold = TRUE) %>%
   row_spec(c(1:5, 10:13, 18:23) - 1, extra_latex_after = "\\rowcolor{gray!6}") %>%
   collapse_rows(columns = 1, latex_hline = "major", 
                 valign = "top")

```

```{r samplesizes_tables_studies}
studies_n <- as.data.frame(table(df_tidy$id), stringsAsFactors = FALSE)
studies_n <- cbind(unique(df_tidy$authors), studies_n)
colnames(studies_n) <- c("Study", "ID", "Effect_sizes")
studies_n <- studies_n %>%
              select(ID, Study, Effect_sizes) %>%
              arrange(-Effect_sizes)

kbl(studies_n, booktabs = TRUE, 
    caption = "Number of effect sizes collected from each of the 34 studies included in the meta-analysis. ID corresponds to the study identification number in our dataset.") %>%
    kable_styling(latex_options = c("striped", "HOLD_position"), 
                                    full_width = FALSE) 
```

```{r samplesizes_tables_moderators, include = TRUE}
# Table for moderator levels
mods <- c("index", "bio", "diversity_source", "environ")
sample_sizes <- do.call(rbind, lapply(mods, function(x) n_studies_entries(df_tidy, x)))
# Format output
sample_sizes <- cbind(row.names(sample_sizes), sample_sizes)
sample_sizes <- as.data.frame(sample_sizes)
names(sample_sizes) <- c("Moderator_levels", "Effect_sizes", "Studies")
sample_sizes$Moderator_levels <- str_replace(sample_sizes$Moderator_levels, "^([a-z])", toupper)
sample_sizes$Moderator_levels[12:16] <- c("Species abundance", "Species diversity",
                                          "Species richness", "Abundance of sounds",
                                          "Diversity of sounds")
sample_sizes$Moderator_levels[18] <- "Non-acoustic"
n_row <- nrow(sample_sizes)
sample_sizes$Moderator_levels[(n_row - 1):n_row] <- c("Aquatic", "Terrestrial")
names(sample_sizes) <- c("Moderator levels", "Effect sizes", "Studies")

kbl(sample_sizes, booktabs = TRUE, row.names = FALSE, 
    caption = "Number of effect sizes and studies per moderator levels.") %>%
    kable_styling(latex_options = c("striped", "HOLD_position"), 
                                    full_width = FALSE) %>%
    row_spec(0, font_size = 12, bold = TRUE) %>%
    pack_rows("Acoustic indices", 1, 11) %>%
    pack_rows("Diversity metrics", 12, 16) %>%
    pack_rows("Diversity source", 17, 18) %>%
    pack_rows("Environment", 19, 20)
```

\begin{figure}[H]
    \includegraphics{"rmd/ps.index.png"}
    \caption{
        Pseudoreplication summary. The data is representing the total number of articles for each index. Color orange represents number of pseudo-replicated studies and green non pseudo-replicated studies. The article (Papin et al., 2019b) was withdrawn from the pseudoreplication analysis due to impossibility of obtaining the pseudoreplication data causing some variation on the total number of each acoustic index.
    }
\end{figure}

\clearpage

\section{Overall Effect Size}

\subsection{Model output}
```{r meta_overall, echo = TRUE}
res_main <- rma.mv(z, var, random = ~1 | id/entry, data = df_tidy)
res_main
```

```{r meta_overall_r}
r_main <- sapply(c(r = res_main$b, CI.lb = res_main$ci.lb, CI.ub = res_main$ci.ub), z2r)
r_main_pander <- r_main
names(r_main_pander) <- c("Estimate", names(r_main)[2:3])
r_main_pander <- as.data.frame(cbind(names(r_main_pander), round(r_main_pander, 2)))
colnames(r_main_pander) <- c("Parameter", "Value")
kbl(r_main_pander, booktabs = TRUE, row.names = FALSE,
    caption = "
        Resulting estimates from intercept-only model converted to Pearson's correlation. 'Estimate' is the Pearson's r summary effect size. 'CI.lb' and 'CI.ub' are the confidence intervals lower and upper bounds, respectively.
    ") %>%
    kable_styling(latex_options = c("striped", "HOLD_position"),
                                    full_width = FALSE) 
```

\subsection{Heterogeneity}

```{r meta_hetero}
Is <- multilevel_I(res_main) * 100
Is_df <- data.frame(Is[1], Is[2])
names(Is_df) <- c("Within study", "Between study")
rownames(Is_df) <- c("% Unexplained variation")
total_I <- paste("Total heterogeneity: ", round(Is[1] + Is[2], 2), "%")
header <- c(3)
names(header) <- c(total_I)
kbl(Is_df, booktabs = TRUE, digits = 2, 
    caption = "
        Uncounted heterogeneity of the intercept-only model as measured by $I^2$ statistic. Within study heterogeneity (level 2) corresponds to the uncounted variation that is found on effect sizes within studies, and between study heterogeneity corresponds to the uncounted variation between studies (level 3).
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

```{r dmetar_I, fig.align = "center", fig.pos = "H", fig.cap = "Visual representation of how variance was distributed over the multilevel structure of the intercept-only model. Within study heterogeneity (level 2) corresponds to the unnacounted variation that is found on effect sizes within studies, and between study heterogeneity corresponds to the unnacounted variation between studies (level 3)."}
mlm.variance.distribution(res_main)
```

\clearpage

\section{Subgroup analysis}

\subsection{Model output}

```{r df_meta_indices, include = FALSE, results = "hide"}
df_indices <-  clear_moderators(df_tidy, "index")
```

```{r meta_indices, echo = TRUE}
res_indices <- rma.mv(z, var, random = ~ 1 | id/entry, mods = ~ index - 1, data = df_indices)
res_indices
```

```{r meta_indices_tbl}
df_pred_indices <- get_predictions(res_indices, intercept = FALSE)
df_pred_indices$coef <- str_remove(df_pred_indices$coef, "index")
names(df_pred_indices) <- c("Index", "Estimate", "SE", "CI.lb", "CI.ub")
kbl(df_pred_indices, booktabs = TRUE, 
    caption = "
        Resulting estimates from sub-group analysis. The 'Estimate' column is the Pearson correlation effect size; SE is the standard error and CI.lb and CI.up; the lower and upper bounds of the confidence intervals, respectively.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

\clearpage

```{r subgroup_plt, fig.pos = "H", fig.cap = "Effect size mean estimates (circles) and corresponding 95% confidence intervals (horizontal lines) obtained from sub-group meta-analysis with acoustic indices as the grouping factor. Estimated effect sizes whose 95% confidence intervals do not overlap zero (black vertical line) indicate a positive correlation between acoustic indices and diversity if they are to the right of zero, or a negative correlation if they are to the left of zero. The dashed green vertical line represents the summary effect size obtained from the intercept only meta-analysis."}
nentries_index <- rowSums(table(df_indices$index, df_indices$id))
nstudies_index <- rowSums(ifelse(table(df_indices$index, df_indices$id) > 0, 1, 0))
n_index <- paste0(nentries_index, " (", nstudies_index, ")")

df_indices_plt <- data.frame("index" = names(nstudies_index),
                             "es" = z2r(res_indices$beta), 
                             "se" = z2r(res_indices$se), 
                             "ci.lb" = z2r(res_indices$ci.lb),
                             "ci.ub" = z2r(res_indices$ci.ub),
                             "n" = nstudies_index)

ggplot(data = df_indices_plt, aes(x = es, y = index)) + 
    geom_point(aes(color = index), size = 4) +
    geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub, color= index),
                   height = 0) + 
    geom_vline(xintercept = 0, linetype = 1) +
    geom_vline(xintercept = z2r(res_main$b), color = "forestgreen", 
               linetype = 2) + 
    scale_y_discrete(limits = rev(df_indices_plt$index)) +
    scale_color_brewer(palette="Dark2") +
    theme_minimal() + 
    xlab("Effect size (r)") +
    theme(axis.text.x = element_text(size = 12, color = "black"),
          axis.text.y = element_text(size = 13, color = "black"),
          axis.line.x = element_line(color = "black"),
          axis.line.y = element_line(color = "black"),
          axis.title.x = element_text(size = 14),
          axis.title.y = element_blank(),
          legend.position = "none"
    )
```

\section{Meta-regression}

\subsection{Model output}

```{r df_meta_regression, include = FALSE, results = "hide"}
mods <- c("index", "bio", "environ", "diversity_source")
df_full <- clear_moderators(df_tidy, mods)
```

```{r meta_regression, echo = TRUE}
res_full <- rma.mv(z, var, random = ~1 | id/entry, 
                   mods = ~ index + bio + environ + diversity_source, 
                   data = df_full)
 
res_full
```

\subsection{Collinearity}

```{r collinearity}
vif_meta <- vif.rma(res_full, table = TRUE)$vif["vif"][-1, , drop = FALSE]
vif_meta <- tibble::rownames_to_column(vif_meta, "Moderators")
colnames(vif_meta)[2] <- "VIF" 
vif_meta$VIF <- round(vif_meta$VIF, 3)
vif_meta$Moderators <- str_remove(vif_meta$Moderators, "index|bio|environ|diversity_source")
vif_meta$Moderators <- final_mod_names(vif_meta$Moderators)
kbl(vif_meta, booktabs = TRUE, 
    caption = "
        VIF values obtained for each moderator level.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

\subsection{Test of moderators}

```{r test_moderators}
imp_mods <- matrix(nrow = length(mods) + 1, ncol = 4, 
                   dimnames = list(NULL, c("Moderator", "Q", "df", "p")))
imp_mods <- as.data.frame(imp_mods)
# Add importance of all moderators
imp_mods[1, 2:ncol(imp_mods)] <- res_full[c("QM", "m", "QMp")]
imp_mods$Moderator[1] <- "All moderators"

for(i in 2:nrow(imp_mods)){
  wald_test <- anova(res_full, 
                     btt=grep(mods[i - 1], rownames(res_full$b)))[c("QM", "m","QMp")]
  imp_mods[i, 2:ncol(imp_mods)] <- wald_test
}
imp_mods$Moderator[2:nrow(imp_mods)] <- c("Acoustic indices", 
                                          "Diversity metrics", 
                                          "Environment", "Diversity source")
imp_mods <- mutate_if(imp_mods, is.numeric, round, 3)

kbl(imp_mods, booktabs = TRUE, 
    caption = "
        Wald-type tests for all moderators (first row), and for each moderator separately (remaining rows). 'Q' is the Wald statistic; 'df' are the degrees of freedom; and 'p' is the probability that moderator estimates came from a chi-square distribution, where all estimates are equal to zero. Thus a p-value < 0.05 gives support against the null hypothesis that moderator levels estimates are equal to zero (i.e. they do not explain variation in effect sizes).
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

\subsection{Contrasts between moderator levels}

\textbf{Contrasts between H and other acoustic indices}
```{r compare_indices_H}
# Test differences between H and other indices
H_comp <- compare_moderators(df_full, res_full, "index", "H")
kbl(H_comp, digits = 3, booktabs = TRUE,
    caption = "
        Wald-type tests for the contrasts between acoustic index H with all other acoustic indices. The column 'Compared' expresses the comparison, in this cases it is the difference between the estimate H and the estimate of each of the other acoustic indices. The column 'Estimate' is the estimate obtained from the difference expressed in the previous column. 'SE' is the standard error of the difference, and CI.lb, CI.up the confidence interval lower and upper bound, respectively. 'QM' is the Wald statistic; 'p' is the probability that the difference between estimates is equal to zero. Thus, a p-value < 0.05 gives support against the null hypothesis of no difference between the estimate of the H index and the estimate of the other index.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

\textbf{Contrasts between NDSI and other acoustic indices}
```{r compare_indices_NDSI}
NDSI_comp <- compare_moderators(df_full, res_full, "index", "NDSI")
kbl(NDSI_comp, digits = 3, booktabs = TRUE,
    caption = "
        Wald-type tests for the contrasts between acoustic index NDSI with all other acoustic indices. The column 'Compared' expresses the difference between the estimate NDSI and the estimate of each of the other acoustic indices. The column 'Estimate' is the estimate obtained from the difference expressed in the previous column; 'SE' is the standard error of the difference, and CI.lb, CI.up the confidence interval lower and upper bound, respectively; 'QM' is the Wald statistic; 'p' is the probability that the difference between estimates is equal to zero. Thus, a p-value < 0.05 gives support against the null hypothesis of no difference between the estimate of the NDSI index and the estimate of the other index.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

\textbf{Contrasts between sound abundance and other biodiversity parameters}
```{r compare_bio}
sound_abund_comp <- compare_moderators(df_full, res_full, "bio", "sound_abundance")
sound_abund_comp$Compared <- c("Abundance of sounds - Species abundance",
                               "Abundance of sounds - Species diversity",
                               "Abundance of sounds - Species richness")
kbl(sound_abund_comp, digits = 3, booktabs = TRUE,
    caption = "
        Wald-type tests for the contrasts between the diversity metric 'abundance of sounds' with all other diversity metrics. The column 'Compared' expresses the difference between the estimate 'abundance of sounds' and the estimate of each of the other diversity metrics. The column 'Estimate' is the estimate obtained from the difference expressed in the previous column; 'SE' is the standard error of the difference, and CI.lb, CI.up the confidence interval lower and upper bound, respectively; 'QM' is the Wald statistic; 'p' is the probability that the difference between estimates is equal to zero. Thus, a p-value < 0.05 gives support against the null hypothesis of no difference between the estimate of the sound abundance metric and the estimate of the other metric.
    ") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = FALSE) 
```

\clearpage

\section{Sensibility analysis}

\subsection{Cook's distance}

```{r cooks_dist_study, fig.height = 6, fig.pos = "h", fig.cap = "Cook's distance values for each study (blue dots) and average Cook's distance over all studies (dashed vertical red line). The Cook's distance for a given study can be interpreted as the distance between the entire set of predicted values once with this study included and once with this study excluded from the model fitting procedure. On the y-axis are the studies identified by first author and year. The x-axis corresponds to the Cook's distance values."}

### Cook's distances for each study!
cooks_dist <- cooks.distance(res_full, cluster=df_full$id)
df_full$id <- as.character(df_full$id)

df_cooks <- data.frame(id = names(cooks_dist), cooks_dist = cooks_dist)

df_cooks <- df_cooks %>% 
              left_join(df_full, by = "id") %>%
              select(id, authors, cooks_dist)
# Remove leading spaces
df_cooks$authors <- str_remove(df_cooks$authors, "^\\s")
df_cooks <- df_cooks %>%
              filter(!duplicated(authors)) %>%
              arrange(authors)

ggplot(data = df_cooks, aes(x = authors, y = cooks_dist, group = 1)) + 
  geom_point(color = "deepskyblue4") +
  geom_line(color = "deepskyblue4") + 
  geom_segment(aes(xend=authors), yend = 0, color = "darkgrey", linetype = 2) + 
  geom_hline(yintercept = mean(cooks_dist), color = "darkred", linetype = 2) + 
  xlab("Studies") + ylab("Cook's Distance") + 
  scale_x_discrete(limits = rev(df_cooks$authors)) + 
  theme_minimal() + 
  theme(
        axis.text = element_text(color = "black"),
        axis.line = element_line(color = "black"),
  ) + 
  coord_flip() 

```

\clearpage

\subsection{Inspection of outliers}

```{r check_outliers, fig.pos = "H", fig.cap = "Boxplot and distribution of effect size values (dots) of the two studies identified as outliers. The y-axis identifies the study, and the x-axis corresponds to the Pearson r effect size. The green vertical dashed line is the summary effect obtained in the intercept-only model."}
outliers <- df_cooks[which(df_cooks$cooks_dist > mean(df_cooks$cooks_dist)), ]$id

df_outliers <- df_full[which(df_full$id %in% outliers), ]

ggplot(data = df_outliers, aes(x = z2r(z), y = id)) + 
  geom_boxplot(aes(color = id), fill = NA, width = 0.3) + 
  geom_jitter(height = 0.1, aes(color = id)) + 
  scale_color_brewer(palette = "Set2") + 
  scale_y_discrete(labels = rev(unique(df_outliers$authors))) + 
  xlab("Effect size (r)") +
  geom_vline(xintercept = z2r(res_main$b), color = "chartreuse4", linetype = 2) + 
  theme_minimal() + 
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_text(size = 11, color = "black"),
    axis.text.x = element_text(size = 11, color = "black"),
    axis.line.x = element_line(color = "black"),
    legend.position = "none"
  )

```

\clearpage

\subsection{Model output without outliers}

```{r df_no_outliers}
df_no_outliers <- df_full[-which(df_full$id %in% outliers), ]
```

```{r no_outliers, echo = TRUE}
res_no_outliers <- rma.mv(z, var, random = ~1 | id/entry, 
                   mods = ~ index + bio + environ + diversity_source, 
                   data = df_no_outliers)
res_no_outliers
```

\subsubsection{Visualization of model estimates with and without outliers}

\vspace{1cm}

```{r outliers_model_plt, fig.cap = "Contrast of model estimates obtained with meta-regression analysis over the full dataset (yellow) and over the dataset with outliers removed (blue). Estimates are represented with circles and corresponding 95% confidence intervals with horizontal lines. Each estimate corresponds to the additive effect when a moderator level is replaced in the intercept (e.g. ADI is the additive effect of ADI when ADI is put as intercept instead of ACI). Estimated effect sizes whose 95% confidence intervals do not overlap zero (black vertical line) indicate a positive correlation between acoustic indices and diversity if they are to the right of zero, or a negative correlation if they are to the left of zero. We considered outliers every study that had a Cook’s distance value higher than the mean of all Cook distances. Model moderators were acoustic indices (ADI, AEI, AR, BIO, H, NDSI, with ACI as intercept), diversity metric (Species abundance, Species diversity, Abundance of sounds, with Species richness as intercept), environment (Aquatic, with Terrestrial as intercept), diversity source (Acoustic, with Non-Acoustic as intercept). The solid vertical black line represents a null effect size."}
df_pred_tbl <- get_predictions(res_full, format_table = TRUE, clean_labels = TRUE)
df_pred_tbl$Coefficients <- final_mod_names(df_pred_tbl$Coefficients)
df_pred <- get_predictions(res_full)
colnames(df_pred) <- tolower(str_remove(colnames(df_pred), "\\s.*"))
df_pred$moderators <- df_pred_tbl$Moderators
df_pred$coef <- factor(df_pred_tbl$Coefficients, 
                       levels = rev(df_pred_tbl$Coefficients))

# With outliers results from full model results 
df_pred$df <- "with_outliers"
# No outliers resuls in dataframe
df_no_outliers_plt <- get_predictions(res_no_outliers)
df_no_outliers_plt$moderators <- df_pred$moderators
df_no_outliers_plt$coef <- factor(df_pred$coef, 
                                  levels = rev(df_pred$coef))
df_no_outliers_plt$df <- "no_outliers"

df_examine_outliers <- rbind(df_pred, df_no_outliers_plt)

plt_colors <- c("skyblue4", "goldenrod3")#"seagreen")
pd <- position_dodge(0.6)
n_rows <- nrow(res_full$b)

ggplot(data = df_examine_outliers, aes(x = estimate, y = coef, color = df, position = df)) + 
    geom_point(position = pd, size = 2.3) +
    geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height = 0, position = pd, size = 0.8) + 
    geom_vline(xintercept = 0, linetype = 1, color = "black") + 
    #scale_y_discrete(labels =  rev(y_labels)) +
    scale_color_manual(values = plt_colors, name = "Dataset", 
                       labels = c("No outliers", "Full dataset")) + 
    geom_hline(yintercept= seq(1, n_rows - 1) + 0.5, linetype = 3, color = "black") + 
    theme_minimal() + 
    xlab("Effect size (r)") +
    theme(axis.text.x = element_text(size = 12, color = "black"),
          axis.text.y = element_text(size = 12, color = "black"),
          axis.line.x = element_line(color = "black"),
          axis.line.y = element_line(color = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_text(size = 14),
          panel.grid.major.y = element_blank(),
          legend.title = element_text(hjust = 0.5, size = 12),
          legend.text = element_text(size = 11),
          legend.position = "top"
    )
```

\clearpage

\subsection{Effect size tendencies}

\textbf{Relationship between effect size and journal impact factor}

```{r effect_size_impact_factor, fig.pos = "H", fig.cap = "Relation between effect size mean values (circles) and journal impact factor. Circle size indicates the relative sample size of each effect size. The fitted line is a simple least squares regression with the corresponding 95% confidence interval region in grey. The dashed horizontal line represents an effect size of 0. Effect size mean values are positioned along the impact factor axis with minor random noise to reduce overlapping."}
plt_color <- "deeppink4"
ggplot(df_tidy, aes(x = impact_factor, y = z2r(z))) + 
  geom_jitter(aes(size = n), shape = 21, 
              fill = alpha(plt_color, 0.5), 
              color = plt_color,
              width = 0.2) + 
    geom_hline(yintercept=0, linetype = 2) +
    geom_smooth(method='lm', color = plt_color) +
    labs(y = "Effect size (r)", x = "Impact Factor") +  
    theme_minimal() +
    theme(
        axis.line.y = element_line(color = "black"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 14),
        legend.position = "none"
    )
```
